SPARQL on the Open, Decentralised Web

### 2016-08-03 dissertation/papersincontext.tex
Caps the titles

\begin{quote}
Kjetil Kjernsmo.
\newblock The necessity of hypermedia rdf and an approach to achieve it.
\newblock In {\em Proceedings of the First Linked APIs workshop at the Ninth
  Extended Semantic Web Conference}, May 2012.
\end{quote}

@@

\begin{quote}
Kjetil Kjernsmo and John~S. Tyssedal.
\newblock Introducing statistical design of experiments to sparql endpoint
  evaluation.
\newblock In Harith Alani, Lalana Kagal, Achille Fokoue, Paul Groth, Chris
  Biemann, Josiane~Xavier Parreira, Lora Aroyo, Natasha Noy, Chris Welty, and
  Krzysztof Janowicz, editors, {\em The Semantic Web – ISWC 2013}, volume
  8219 of {\em Lecture Notes in Computer Science}, pages 360--375. Springer
  Berlin Heidelberg, 2013.
\end{quote}

@@

\begin{quote}
Gregory~Todd Williams and Kjetil Kjernsmo.
\newblock Pushing complexity down the stack.
\newblock In {\em Proceedings of the ISWC Developers Workshop 2014}, volume
  1268 of {\em {CEUR} Workshop Proceedings}. CEUR-WS.org, May 2014.
\end{quote}

@@

\begin{quote}
Kjetil Kjernsmo.
\newblock A survey of http caching implementations on the open semantic web.
\newblock In Fabien Gandon, Marta Sabou, Harald Sack, Claudia d’Amato,
  Philippe Cudré-Mauroux, and Antoine Zimmermann, editors, {\em The Semantic
  Web. Latest Advances and New Domains}, volume 9088 of {\em Lecture Notes in
  Computer Science}, pages 286--301. Springer International Publishing, 2015.
\end{quote}

>>>>

\begin{quote}
Kjetil Kjernsmo.
\newblock The Necessity of Hypermedia RDF and an Approach to Achieve it.
\newblock In {\em Proceedings of the First Linked APIs workshop at the Ninth
  Extended Semantic Web Conference}, May 2012.
\end{quote}

@@

\begin{quote}
Kjetil Kjernsmo and John~S. Tyssedal.
\newblock Introducing Statistical Design of Experiments to SPARQL Endpoint
  Evaluation.
\newblock In Harith Alani, Lalana Kagal, Achille Fokoue, Paul Groth, Chris
  Biemann, Josiane~Xavier Parreira, Lora Aroyo, Natasha Noy, Chris Welty, and
  Krzysztof Janowicz, editors, {\em The Semantic Web – ISWC 2013}, volume
  8219 of {\em Lecture Notes in Computer Science}, pages 360--375. Springer
  Berlin Heidelberg, 2013.
\end{quote}

@@

\begin{quote}
Gregory~Todd Williams and Kjetil Kjernsmo.
\newblock Pushing Complexity Down the Stack.
\newblock In {\em Proceedings of the ISWC Developers Workshop 2014}, volume
  1268 of {\em {CEUR} Workshop Proceedings}. CEUR-WS.org, May 2014.
\end{quote}

@@

\begin{quote}
Kjetil Kjernsmo.
\newblock A Survey of HTTP Caching Implementations on the Open Semantic Web.
\Newblock In Fabien Gandon, Marta Sabou, Harald Sack, Claudia d’Amato,
  Philippe Cudré-Mauroux, and Antoine Zimmermann, editors, {\em The Semantic
  Web. Latest Advances and New Domains}, volume 9088 of {\em Lecture Notes in
  Computer Science}, pages 286--301. Springer International Publishing, 2015.
\end{quote}
